---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cocktailtools

The goal of `cocktailtools` is to provide simple tools for exploring and checking cocktail datasets. The package includes a data-quality helper function and a custom `ggplot2` theme designed for cocktail-related visualizations.

## Installation

You can install the development version of `cocktailtools` from GitHub:

```{r, eval=FALSE}
pak::pak("sjk026-afk/cocktailtools")
```

# cocktailtools

The goal of `cocktailtools` is to provide simple tools for exploring and checking cocktail datasets. The package uses the TidyTuesday cocktail dataset and includes a data-quality helper function and a custom `ggplot2` theme designed for cocktail-related visualizations.

## What the Package Does

`cocktailtools` includes two main functions:

- `cocktail_check()` provides a quick check of a cocktail dataset by reporting the number of unique cocktails and ingredients, missing ingredients and measurements, and duplicate rows.
- `theme_cocktail()` provides a custom `ggplot2` theme with a clean cocktail-inspired design for visualizations.

The package is designed to make basic data exploration easier while giving cocktail-related visualizations a consistent appearance.

## Data Exploration

The package vignette demonstrates how `cocktailtools` can be used to explore the cocktail dataset. The analysis uses common data manipulation techniques including filtering, grouping and summarizing, joining, arranging, and creating new variables with `mutate()`.

For example, the data can be grouped by ingredient to determine which ingredients appear in the greatest number of cocktails.

## Visualization

`theme_cocktail()` can be added to a `ggplot2` visualization to give plots a consistent appearance.

```{r}
cocktails %>%
  count(category, sort = TRUE) %>%
  ggplot(aes(x = reorder(category, n), y = n)) +
  geom_col(fill = "#264653") +
  coord_flip() +
  labs(
    title = "Cocktails by Category",
    x = "Category",
    y = "Number of Rows"
  ) +
  theme_cocktail()
```
## Design and Accessibility
The package uses a customized brand.yml file to create a consistent visual identity for cocktailtools. The color palette uses dark teal, teal, gold, coral, and cream to create a cocktail-inspired appearance while keeping the design clean and readable. Darker colors are used for important text and visual elements to improve contrast and accessibility.



